---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sGMYC

<!-- badges: start -->
<!-- badges: end -->

The functions in sGMYC allow to subsample sequences within
species to run a single-threshold GMYC analysis (citation) with subsamples of sequences obtained from within the species delimited using all sequences. It also plots a heatmap of 
the probabilities of conspecificity among samples based on
funtions of the bGMYC package (citation).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("arleyc/sGMYC")
```
## Example

```{r example1}
library(sGMYC)
#Species delimitation...
```

## References

GMYC

bGMYC

## Citation

de Magalhães RF, Santos MTT & Camargo A. 2024. Subsampling GMYC (sGMYC): a new algorithmic implementation of the generalized mixed Yule-coalescent model. I Congresso Brasileiro de Biologia Evolutiva, Curitiba, Brasil.
