---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sGMYC: GMYC analysis with subsampling

<!-- badges: start -->
<!-- badges: end -->

sGMYC runs a single-threshold GMYC analysis (Pons et al. 2006) using the splits package (Fujisawa & Barraclough 2013) with 
subsamples of sequences obtained from within the species 
delimited using all sequences. It also plots a heatmap of 
conspecificity probabilities among samples based on functions 
of the bGMYC package (Reid & Carstens 2012). When more than one tree are provided, sGMYC can implement the analysis with multiple cores using the parallel and doParallel packages.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("arleyc/sGMYC")
```
## Example 1: subsampling from one tree

```{r example1}
library(sGMYC)

data("hypotree")

sGMYC(hypotree,nreps=10)

#Plotting heatmap of conspecificity probabilities

```

```{r example2}
#Species delimitation with subsampling using multiple trees and computer cores

#Plotting heatmap of conspecificity probabilities
```

## References

Fujisawa T & Barraclough TG. 2013. Delimiting species using single-locus data and the Generalized Mixed Yule Coalescent approach: A revised method and evaluation on simulated data sets. Systematic Biology 62:707–724, doi: 10.1093/sysbio/syt033

Pons J, Barraclough TG, Gomez-Zurita J, Cardoso A, Duran DP, Hazell S, Kamoun S, Sumlin WD & Vogler AP. 2006. Sequence-based species delimitation for the DNA taxonomy of undescribed insects. Systematic Biology 55:595-609, doi: 10.1080/10635150600852011.

Reid NM & Carstens BC. 2012. Phylogenetic estimation error can decrease the accuracy of species delimitation: a Bayesian implementation of the general mixed Yule-coalescent model. BMC Evolutionary Biology 12:196, doi: 10.1186/1471-2148-12-196.

## Citation

de Magalhães RF, Santos MTT & Camargo A. 2024. Subsampling GMYC (sGMYC): a new algorithmic implementation of the generalized mixed Yule-coalescent model. I Congresso Brasileiro de Biologia Evolutiva, Curitiba, Brasil.
